---
title: "Fars functions details"
author: "Jose Coello"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{details}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#library(trypackage)
```

# Description

This package will be using data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.

This package has five functions:

1. fars_read: This is a function that reads data from US National Highway Traffic Safety Administration's found in the working directory.

2. make_filename: This function creates the name of the US National Highway Traffic Safety Administration's data set for the selected year.

3. fars_read_years: This function reads data from the US National Highway Traffic Safety Administration and returns the variables month and year.

4. fars_summarize_years: This function summarizes fatal injuries sustained in motor vehicle traffic accidents by month.

5. fars_map_state: This function graphs the latitude and longitud of the selected state.

# Example

```{r}
# year <- make_filename(year = 2013)
# 
# data <- fars_read(filename = year)
# 
# data2 <- fars_read_years(2013)
# 
# data3 <- fars_summarize_years(years = 2013)
# 
# fars_map_state(state.num = 1, year = 2013)
```


